\papertitle

### 2014-03-20 final-report/paper.tex
intro changes

\item A view for communication between workers. A directed link between two fragments in the physical query plan DAG
represents source workers sending tuples to destination workers. Upon clicking on a link, the visualization renders the
\network view. This shows the aggregate number of tuples exchanged between workers as well as a time series
charting the number of tuples exchanged over time.

>>>>

\item \emph{How is the input data partitioned?}
Data skew is an important problem in a DDBMS, which can result in uneven communication between worker threads
residing on different machines. \system provides a view for \network that represents communication   
between two fragments in the \graph.

%represents source workers sending tuples to destination workers. Upon clicking on a link, the visualization renders the
%\network view. This shows the aggregate number of tuples exchanged between workers as well as a time series
%charting the number of tuples exchanged over time.
